%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\definecolor{darkcyan}{rgb}{0, 0.4, 0.8}    % Define darker blue
\usepackage[colorlinks=true, linkcolor={0,0,0.5}, urlcolor=darkcyan]{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Nathan Hutton}\\
    LinkedIn : \href{https://www.linkedin.com/in/nathanhutton/}{www.linkedin.com/in/nathanhutton/} & Email : \href{mailto:nathan.d.hutton@gmail.com}{nathan.d.hutton@gmail.com}\\
    Portfolio : \href{https://nathan-hutton.github.io/Portfolio/}{nathan-hutton.github.io/Portfolio} & GitHub : \href{https://github.com/Nathan-Hutton}{github.com/Nathan-Hutton}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Utah}{SLC, UT}
      {Master of Computer Graphics and Data Visualization | GPA: 4.0}{Dec. 2025}
    \resumeSubheading
      {Westminster University}{SLC, UT}
      {Bachelor of Computer Science |  GPA: 4.0}{May. 2024}
      \begin{itemize}[after=\vspace{-1em}]
          \small 
          \itemsep 0.0em
          \item Applied mathematics minor.
          \item Received the outstanding computer science student of the year award.
      \end{itemize}
    \resumeSubheading
      {Salt Lake Community College}{SLC, UT}
      {Associate of Science | GPA: 4.0}{May. 2021}
      \begin{itemize}[after=\vspace{-1em}]
          \small 
          \itemsep 0.0em
          \item Earned degree while in high school.
      \end{itemize}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  	\resumeSubheading
	  {Flight Safety International}{Broken Arrow, OK}
	  {Software Engineer Intern}{May. 2025 - Aug. 2025}

    \resumeSubheading
      {Idaho National Laboratory}{SLC, UT}
      {Software Engineer Intern}{Feb. 2023 - May. 2024}
      \begin{itemize}[before=\vspace{-0.85em},after=\vspace{-1em}]
          \small 
          \itemsep 0.0em
          \item Debug and reformat C++, C, and Python code.
          \item Work with waveform code on Linux.
          \item Convert Matlab test harness to Python.
          \item Configure CI/CD pipelines.
          \item Implement GUIs which interface with a backend.
          \item Converted documents made in LibreOffice to Latex documents.
      \end{itemize}

    \resumeSubheading
      {Westminster University}{SLC, UT}
      {Computer Science Tutor/TA}{Aug. 2022 - Dec. 2023}
      \begin{itemize}[before=\vspace{-0.85em},after=\vspace{-1em}]
          \small 
          \item Guide computer science students through computer science and algorithms classes.
      \end{itemize}

    \resumeSubheading
      {Westminster University}{SLC, UT}
      {IT Technician}{Aug. 2021 - May. 2024}
      \begin{itemize}[before=\vspace{-0.85em},after=\vspace{-1em}]
          \small 
          \item Help Westminster students and faculty with technical issues over the phone and in person.
      \end{itemize}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
	\resumeSubItem{\href{https://github.com/Nathan-Hutton/boids}{Boids Flocking Simulation} [\href{https://www.youtube.com/watch?v=AMXlc43AJDk}{Demo Video}]}
	{OpenGL flocking simulation in C++. A simple ruleset by Craig Reynolds leads to complex flocking behavior. Uses IMGui, color blending using HSB colorspace, and obstacle avoidance.}
	\resumeSubItem{\href{https://github.com/Nathan-Hutton/solar-system}{Solar System} [\href{https://www.youtube.com/watch?v=KRmn0imU6Xk}{Demo Video}]}
      {Simulation of a solar system using OpenGL/C++ with dynamic physics. Utilizes smooth shading, shadow mapping, texture mapping, model importing, Blinn-Phong Lighting, HDR, skyboxes, verlet numerical integration, time/speed manipulation, and bloom.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Ray-Tracer}{Ray Tracer}}
      {Python program replicating the physics of light to create an image. Functionally for smooth
shading, triangle meshes, Phong lighting, point and directional lights, shadows, and transformations. Made with minimal reliance on third-party libraries.}
    \resumeSubItem{\href{https://github.com/CharlesBirdgv/Squibblets}{Squibblets}}
      {4-person team Unity project using AGILE. I made 54\% of all commits and created the main
gameplay loop, movement, online leaderboards, audio, AI, UI, menus, and more. Also significantly
contributed to code organization and bug fixes.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Minijava_Compiler_AST}{Minijava Compiler}}
    {Compiler created in Java with features such as type-checking, lexing and parsing
with ANTLR4, JVM assembly code generation, AST generation, class and block structure (flow control),
print statements, package inclusion, and method calls.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Chatroom}{Java Chatroom}}
    {Terminal based chatroom utilizing java.net. Features include broadcast messages, private messages, user list retrieval, and notifications when users join or leave.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Flight-Finder}{Cheap Flight Tracker}}
    {Python app which interfaces with an API to find cheap flights to locations the user
specifies. Dynamically updates a spreadsheet with flight info and sends the user a text message.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \textbf{Languages}{: C++, Python, C, Java, C\#, Javascript}
 \hfill
 \textbf{Tech}{: OpenGL, Linux, Docker, Gitlab CI/CD, D3}

%-------------------------------------------
\end{document}

