%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{xcolor}
\definecolor{darkcyan}{rgb}{0, 0.4, 0.8}    % Define darker blue
\usepackage[colorlinks=true, linkcolor={0,0,0.5}, urlcolor=darkcyan]{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Nathan Hutton}\\
    LinkedIn : \href{https://www.linkedin.com/in/nathanhutton/}{https://www.linkedin.com/in/nathanhutton/} & Email : \href{mailto:nathan.d.hutton@gmail.com}{nathan.d.hutton@gmail.com}\\
    Portfolio : \href{https://nathan-hutton.github.io/Portfolio/}{https://nathan-hutton.github.io/Portfolio} & GitHub : \href{https://github.com/Nathan-Hutton}{https://github.com/Nathan-Hutton}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Utah}{Salt Lake City, UT}
      {Master of Computer Science}{Aug. 2024 -- May. 2026}
    \resumeSubheading
      {Westminster University}{Salt Lake City, UT}
      {Bachelor of Computer Science;  GPA: 4.0}{Aug. 2021 -- May. 2024}
      \begin{itemize}[after=\vspace{-1em}]
          \small 
          \itemsep 0.0em
          \item Applied mathematics minor.
          \item Received the outstanding computer science student of the year award.
      \end{itemize}
    \resumeSubheading
      {Salt Lake Community College}{Salt Lake City, UT}
      {Associate of Science: GPA: 4.0}{Aug. 2021 -- May. 2024}
      \begin{itemize}[after=\vspace{-1em}]
          \small 
          \itemsep 0.0em
          \item Earned degree while in high school.
      \end{itemize}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Idaho National Laboratory}{Salt Lake City, UT}
      {Software Engineer Intern}{Feb 2023 - May 2024}
      \begin{itemize}[before=\vspace{-0.85em},after=\vspace{-1em}]
          \small 
          \itemsep 0.0em
          \item Debug and reformat C++, C, and Python code.
          \item Work with waveform code on Linux.
          \item Convert Matlab test harness to Python.
          \item Configure CI/CD pipelines.
          \item Implement GUIs which interface with a backend.
          \item Converted documents made in LibreOffice to Latex documents.
      \end{itemize}

    \resumeSubheading
      {Westminster University}{Salt Lake City, UT}
      {Computer Science Tutor/TA}{Aug 2022 - Dec 2023}
      \begin{itemize}[before=\vspace{-0.85em},after=\vspace{-1em}]
          \small 
          \item Guide computer science students through computer science and algorithms classes.
      \end{itemize}

    \resumeSubheading
      {Westminster University}{Salt Lake City, UT}
      {IT Technician}{Aug 2021 - May 2024}
      \begin{itemize}[before=\vspace{-0.85em},after=\vspace{-1em}]
          \small 
          \item Help Westminster students and faculty with technical issues over the phone and in person.
      \end{itemize}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/solar-system}{Solar System}}
      {Simulation of a solar system using OpenGL/C++ with dynamic physics. Includes smooth
shading, shadow mapping, texture mapping, model importing, Blinn-Phong Lighting, HDR, skyboxes, second order numerical integration, time/speed manipulation, and optimized bloom. Here's a \href{https://nathan-hutton.github.io/Portfolio/images/finalVideo.mp4}{demo video}.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Ray-Tracer}{Ray Tracer}}
      {Python program replicating the physics of light to create an image. Functionally for smooth
shading, triangle meshes, Phong lighting, point and directional lights, shadows, and transformations. Made with minimal reliance on third-party libraries.}
    \resumeSubItem{\href{https://github.com/CharlesBirdgv/Squibblets}{Squibblets}}
      {4-person team Unity project using AGILE. I made 54\% of all commits and created the main
gameplay loop, movement, online leaderboards, audio, AI, UI, menus, and more. Also significantly
contributed to code organization and bug fixes.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Minijava_Compiler_AST}{Minijava Compiler}}
    {Compiler created in Java with features such as type-checking, lexing and parsing
with ANTLR4, JVM assembly code generation, AST generation, class and block structure (flow control),
print statements, package inclusion, and method calls.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Chatroom}{Java Chatroom}}
    {Terminal based chatroom utilizing java.net. Features include broadcast messages, private messages, user list retrieval, and notifications when users join or leave.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Flight-Finder}{Cheap Flight Tracker}}
    {Python app which interfaces with an API to find cheap flights to locations the user
specifies. Dynamically updates a spreadsheet with flight info and sends the user a text message.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Bitmap-Editor}{Bitmap Editor}}
    {Bitmap photo editor in C. Functionality includes conversion to grayscale, image reflection, posterization, squashing, mirroring, shrinking, rotation, and skewing.}
    \resumeSubItem{\href{https://github.com/Nathan-Hutton/Asteroids}{Asteroids}}
    {Recreation of Asteroids in Java. Features include dynamic asteroid creation, splitting asteroids into smaller asteroids when shot, alien ship opponent, movement, and a life system.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C++, Python, C, Java, C\#, SQL}
     \hfill
     \textbf{Technologies}{: OpenGL, Linux, Docker, Gitlab CI/CD}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

